---
title: "Compabs"
author: "Cameron Holdaway, Will McCarthy"
date: "09/21/2020"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
library(lme4)
# library(arm)
# library(xtable)
library(lmerTest)
library(tidyboot)
theme_set(theme_classic())
theme_update(# axis labels
  axis.title = element_text(size = 28),
  # tick labels
  axis.text = element_text(size = 24),
  # title 
  title = element_text(size = 24),
  legend.position = 'FALSE', 
  text = element_text(size=16), 
  element_line(size=1), 
  element_rect(size=2, color="#00000"))

primary_color = '#21606C'
secondary_color = '#22AAAA'
```

#### Read data, as output by compabs_analysis_df_generator.ipynb
```{r}
# import dataframes
df_block = read.csv('../results/csv/df_block.csv')
df_chat = read.csv('../results/csv/df_chat.csv')
df_trial = read.csv('../results/csv/df_trial.csv')
df_exit = read.csv('../results/csv/df_exit.csv')

df_block$repNum = as.numeric(as.character(df_block$repNum))
df_chat$trialNum = as.numeric(as.character(df_chat$trialNum))
df_chat$repNum = as.numeric(as.character(df_chat$repNum))

#Group stimuli into scenes
df_trial = df_trial %>%
    dplyr::mutate(towerSet = case_when((leftTarget == 'L' | rightTarget == 'L')
                              & (leftTarget == 'Pi' | rightTarget == 'Pi')~ 'L/Pi',
                                (leftTarget == 'L' | rightTarget == 'L')
                            & (leftTarget == 'C' | rightTarget == 'C') ~ 'L/C', TRUE~'C/Pi'))
df_block = df_block %>%
    dplyr::mutate(towerSet = case_when((leftTarget == 'L' | rightTarget == 'L')
                              & (leftTarget == 'Pi' | rightTarget == 'Pi')~ 'L/Pi',
                                (leftTarget == 'L' | rightTarget == 'L')
                            & (leftTarget == 'C' | rightTarget == 'C') ~ 'L/C', TRUE~'C/Pi'))
df_trial$trialNum = as.numeric(as.character(df_trial$trialNum))
df_trial$repNum = as.numeric(as.character(df_trial$repNum)) +1

```

#### Filter trials that don't reach criterion
```{r}
#How many dyads fulfill 75% Accuracy on 75% of trials
games75 = df_trial %>% 
  group_by(gameid, trialNum) %>% 
  filter(trialScore > 75  & repNum != 'practice') %>%
  group_by(gameid)%>% 
  tally %>% 
  filter(n/12 >=0.75) %>% 
  distinct(gameid)

#How many dyads said they were confused <-- this is probably inverse coded...
gamesConfused = df_exit %>% 
  filter(confused == 'yes') %>% 
  distinct(gameid)

#How many dyads said they spoke English
gamesEnglish = df_exit %>% 
  filter(nativeEnglish == 'yes') %>% 
  distinct(gameid)

gamesToKeep = intersect(games75, gamesConfused, gamesEnglish)$gameid
```

#### Filter trials that don't reach criterion
```{r}
df_trial <- df_trial %>% 
  filter(!is.na(trialNum)) %>% 
  subset(gameid %in% gamesToKeep)

df_chat <- df_chat %>% 
  filter(!is.na(trialNum)) %>% 
  subset(gameid %in% gamesToKeep)

df_block <- df_block %>% 
  filter(!is.na(trialNum)) %>% 
  subset(gameid %in% gamesToKeep)

df_exit <- df_exit %>% 
  subset(gameid %in% gamesToKeep)
```

## Performance

### Accuracy 

#### Accuracy across reps

```{r}
acc.boot <- df_trial %>%
  group_by(repNum) %>%
  tidyboot_mean(column=trialScore, nboot=100)
acc.boot
```


```{r}
acc.boot %>%
  ggplot(aes(x=repNum, y=empirical_stat)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                  data = acc.boot, color = primary_color) +  
    geom_line(size=1.5, color = primary_color)+
    geom_point(size = 4, color = primary_color) +
    ylab("accuracy (F1)") +
    xlab("repetition") +
    theme_few() +
    # scale_x_continuous(breaks = round(seq(1, 4, by =1),1)) +
    ylim(c(50,100)) +
    xlim(c(0.75,4.25)) +
    scale_y_continuous(limits = c(50,100), breaks = c(50,60,70,80,90,100),labels=c('0.5','0.6','0.7','0.8','0.9','1.0')) +
    # scale_y_continuous(breaks = seq(-0.5,2.5,0.5)) +
    ggtitle('builder accuracy') +
    theme(legend.position = 'FALSE', text = element_text(size=16), element_line(size=1), plot.title = element_text(hjust = 0.5, size=16), element_rect(size=2, color="#00000"))
ggsave('../results/plots/ORLR/CA_ORLR20_F1_reps.pdf', width=7, height = 11, units='cm', useDingbats = F)
```
```{r}
df_trial$perfect <- as.numeric(df_trial$trialScore == 100)

perf.boot <- df_trial %>%
  group_by(repNum) %>% 
  tidyboot_mean(column=perfect, nboot=100)

perf.boot
```
```{r}
m.acc = lmer(data = df_trial, trialScore  ~ repNum + (1 | gameid))
summary(m.acc)
```


```{r}
perf.boot %>%
  ggplot(aes(x=repNum, y=empirical_stat)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                  data = perf.boot, color=primary_color) +  
    geom_line(size=1.5, color=primary_color)+
    geom_point(size = 4, color=primary_color) +
    ylab("Proportion trials perfect") +
    xlab("Repetition") +
    theme_few() +
    # scale_x_continuous(breaks = round(seq(1, 4, by =1),1)) +
    xlim(c(0.75,4.25)) +
    ylim(c(0.4,1)) +
    #scale_x_continuous(limits = c(0.6,4.4), breaks = c(1,2,3,4),labels=c('first', '2nd','3rd','final')) +
    # scale_y_continuous(breaks = seq(-0.5,2.5,0.5)) +
    ggtitle('perfect trials') +
    theme(legend.position = 'FALSE', text = element_text(size=16), element_line(size=1), plot.title = element_text(hjust = 0.5, size=16), element_rect(size=2, color="#00000"))

```

```{r}
m.acc = glmer(data = df_trial, family = 'binomial',  perfect ~ repNum + (1 + repNum | gameid))
summary(m.acc)
```


### Word Count 

#### Word count across trials
```{r}
wc.boot <- df_trial %>%
  group_by(repNum) %>%
  tidyboot_mean(column=word_count, nboot=100)
wc.boot
```


```{r}
wc.boot %>%
  ggplot(aes(x=repNum,y=empirical_stat)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                  data = wc.boot, color = primary_color) +  
    geom_line(size=1.5, color = primary_color)+
    geom_point(size = 4, color = primary_color) +
    ylab("words") +
    xlab("repetition") +
    theme_few() +
    # scale_x_continuous(breaks = round(seq(1, 4, by =1),1)) +
    xlim(c(0.5,4.5)) +  
    ylim(c(0,70)) +
    #scale_x_continuous(limits = c(0.6,4.4), breaks = c(1,2,3,4),labels=c('first', '2nd','3rd','final')) +
    # scale_y_continuous(breaks = seq(-0.5,2.5,0.5)) +
    ggtitle('words per trial') +
    theme(legend.position = 'FALSE', text = element_text(size=16), element_line(size=1), plot.title = element_text(hjust = 0.5, size=16), element_rect(size=2, color="#00000"))
ggsave('../results/plots/ORLR/CA_ORLR20_word_count_reps.pdf', width=7, height = 11, units='cm', useDingbats = F)
```

```{r}
# Using || gets rid of correlations in random effects (not maximal model anymore)
m.wc = lmer(data = df_trial, word_count ~ repNum + (1 + repNum || gameid) + (1 | towerSet))
summary(m.wc)

```

### Character Count 

#### Character count across trials
```{r}
cc.boot <- df_trial %>%
  group_by(repNum) %>%
  tidyboot_mean(column=char_count, nboot=100)
cc.boot
```


```{r}
cc.boot %>%
  ggplot(aes(x=repNum,y=empirical_stat)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                  data = cc.boot, color = primary_color) +  
    geom_line(size=1.5, color = primary_color)+
    geom_point(size = 4, color = primary_color) +
    ylab("characters") +
    xlab("repetition") +
    theme_few() +
    # scale_x_continuous(breaks = round(seq(1, 4, by =1),1)) +
    xlim(c(0.75,4.25)) +
    ylim(c(0,350)) +
    ggtitle('characters per trial') +
    #scale_x_continuous(limits = c(0.6,4.4), breaks = c(1,2,3,4),labels=c('first', '2nd','3rd','final')) +
    # scale_y_continuous(breaks = seq(-0.5,2.5,0.5)) +
    theme(legend.position = 'FALSE', text = element_text(size=16), element_line(size=1), plot.title = element_text(hjust = 0.5, size=16), element_rect(size=2, color="#00000"))
ggsave('../results/plots/ORLR/CA_ORLR20_char_count_reps.pdf', width=7, height = 11, units='cm', useDingbats = F)
```

```{r}
m.cc = lmer(data = df_trial, char_count ~ repNum + (1 + repNum || gameid) + (1 | towerSet))
summary(m.cc)
```


### Num messages 

#### Number of messages across trials
```{r}
mess.boot <- df_trial %>%
  group_by(repNum) %>%
  tidyboot_mean(column=n_messages, nboot=100)
mess.boot
```

```{r}
mess.boot %>%
  ggplot(aes(x=repNum, y=empirical_stat)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                  data = mess.boot, color = primary_color) +  
    geom_line(size=1.5, color = primary_color)+
    geom_point(size = 4, color = primary_color) +
    ylab("messages") +
    xlab("repetition") +
    theme_few() +
    # scale_x_continuous(breaks = round(seq(1, 4, by =1),1)) +
    xlim(c(0.75,4.25)) +
    # ylim(c(1,7)) +
    #scale_x_continuous(limits = c(1,6), breaks = c(1,2,3,4),labels=c('first', '2nd','3rd','final')) +
    scale_y_continuous(limits = c(1,6), breaks = c(1,2,3,4,5,6),labels=c(' 1', ' 2',' 3',' 4',' 5',' 6')) +
    ggtitle('messages per trial') +
    theme(legend.position = 'FALSE', text = element_text(size=16), element_line(size=1), plot.title = element_text(hjust = 0.5, size=16), element_rect(size=2, color="#00000"))
ggsave('../results/plots/ORLR/CA_ORLR20_messages_reps.pdf', width=7, height = 11, units='cm', useDingbats = F)
```

```{r}
m.mes = lmer(data = df_trial, n_messages ~ repNum + (1 + repNum || gameid) + (1 | towerSet))
summary(m.mes)
```

### Timing 

Have to exclude participants marked as 'flagged', as techical errors/ connectivity issues mean they had some negative block placement times.

#### Total time to send messages across trials
```{r}
chat.time.boot <- df_trial %>%
  group_by(repNum) %>%($b=$, $t=$, $p<0.0001$)
  tidyboot_mean(column=total_chat_duration, nboot=100)
chat.time.boot
```

```{r}
chat.time.boot %>%
  ggplot(aes(x=repNum, y=empirical_stat)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,color = primary_color) +  
    geom_line(size=1.5, color = primary_color)+
    geom_point(size = 4, color = primary_color) +
    ylab("total chat duration (s)") +
    xlab("repetition") +
    theme_few() +
    # scale_x_continuous(breaks = round(seq(1, 4, by =1),1)) +
    # xlim(c(0.5,4.5)) +  
    # ylim(c(0,7)) +
    #scale_x_continuous(limits = c(0.6,4.4), breaks = c(1,2,3,4),labels=c('first', '2nd','3rd','final')) +
    scale_y_continuous(limits = c(40000,200000), labels = c('40','60','120','160','200')) +
    ggtitle('messaging time') +
    theme(legend.position = 'FALSE', text = element_text(size=16), element_line(size=1), plot.title = element_text(hjust = 0.5, size=16), element_rect(size=2, color="#00000"))
ggsave('../results/plots/ORLR/CA_ORLR20_chat_duration_reps.pdf', width=7, height = 11, units='cm', useDingbats = F)
```

```{r}
m.chat.time = lmer(data = df_trial, total_chat_duration ~ repNum + (1 + repNum | gameid) + (1 | towerSet))
summary(m.chat.time)
```



#### Total time to send messages across trials
```{r}
block.time.boot <- df_trial %>%
  group_by(repNum) %>%
  tidyboot_mean(column=total_block_duration, nboot=100)
```

```{r}
block.time.boot %>%
  ggplot(aes(x=repNum, y=empirical_stat)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5, color = primary_color) +  
    geom_line(size=1.5, color = primary_color)+
    geom_point(size = 4, color = primary_color) +
    ylab("total build duration") +
    xlab("repetition") +
    theme_few() +
    # scale_x_continuous(breaks = round(seq(1, 4, by =1),1)) +
    # xlim(c(0.5,4.5)) +  
    # ylim(c(0,7)) +
    #scale_x_continuous(limits = c(0.6,4.4), breaks = c(1,2,3,4),labels=c('first', '2nd','3rd','final')) +
    # scale_y_continuous(breaks = seq(-0.5,2.5,0.5)) +
    theme(legend.position = 'FALSE', text = element_text(size=16), element_line(size=1), element_rect(size=2, color="#00000"))

```

```{r}
m.block.time = lmer(data = df_trial, total_block_duration ~ repNum + (1 + repNum | gameid) + (1 | towerSet))
summary(m.block.time)
```



```{r}

df_ref = read_csv('justin_julia_tag.csv')
df_ref = df_ref[complete.cases(df_ref), ]
df_ref$repNum = df_ref$repNum +1
#df$block_diff = df$block_justin - df$block_julia
#mean(df$block_diff)
#hist(df$block_diff)

#df = df %>%  filter(repNum == 3 | repNum == 0)

lin = lm(data = df_ref, refExp ~ repNum*rater*expType)
summary(lin)

# interaction = df_ref %>% 
#   group_by(repNum, expType) %>% 
#   summarise(mu = mean(refExp), sd = sd(refExp), n = n(), sem = sd(refExp)/sqrt(n()))
# glimpse(interaction)

```

```{r}
ref.boot <- df_ref %>%
  group_by(repNum, expType) %>%
  tidyboot_mean(column=refExp, nboot=1000)
ref.boot
```

```{r}
ggplot(ref.boot, aes(x=repNum, y=empirical_stat, colour=expType)) + geom_line(size = 1.5)+
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1.5)+
  geom_point(size = 4) +
  theme_few() +
  xlab("repetition")+
  ylab("referring expressions")+
  theme(legend.position = 'FALSE', text = element_text(size=16),
        element_line(size=1),
        element_rect(size=2, color="#00000"))+
  scale_color_manual(values=c("#303030","#9D9D9D")) +
  xlim(c(0.75,4.25)) +
  ylim(c(0, 1.65)) +
  # scale_y_continuous(limits = c(1,6), breaks = c(1,2,3,4,5,6),labels=c(' 1', ' 2',' 3',' 4',' 5',' 6')) +
  ggtitle('referring expressions') +
  theme(legend.position = 'FALSE', text = element_text(size=16), element_line(size=1), plot.title = element_text(hjust = 0.5, size=16), element_rect(size=2, color="#00000"))
ggsave('../results/plots/ORLR/CA_ORLR20_ref_exp.pdf', width=7, height = 11, units='cm', useDingbats = F)
```


```{r}
ggplot(interaction, aes(x=repNum, y=mu, colour=expType)) + geom_line(size = 1.5)+
  geom_errorbar(aes(ymin=mu-sem, ymax=mu+sem), width = 0, size = 1.5)+
  geom_point(size = 4) +
  theme_few() +
  xlab("repetition")+
  ylab("referring expressions")+
  theme(legend.position = 'FALSE', text = element_text(size=16),
        element_line(size=1),
        element_rect(size=2, color="#00000"))+
  scale_color_manual(values=c("#151515","#7D7D7D")) +
  xlim(c(0.75,4.25)) +
  ylim(c(0, 1.6)) +
  # scale_y_continuous(limits = c(1,6), breaks = c(1,2,3,4,5,6),labels=c(' 1', ' 2',' 3',' 4',' 5',' 6')) +
  ggtitle('referring expressions') +
  theme(legend.position = 'FALSE', text = element_text(size=16), element_line(size=1), plot.title = element_text(hjust = 0.5, size=16), element_rect(size=2, color="#00000"))
#ggsave('../results/plots/ORLR/CA_ORLR20_test_ref_exp.pdf', width=7, height = 11, units='cm', useDingbats = F)
```

```{r}

```
