---
title: "Compabs"
author: "Cameron Holdaway"
date: "7/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
library(lme4)
# library(arm)
# library(xtable)
library(lmerTest)
theme_set(theme_classic())
theme_update(# axis labels
             axis.title = element_text(size = 28),
             # tick labels
             axis.text = element_text(size = 24),
             # title 
             title = element_text(size = 50))

```
#### Start by reading in the data (CSV compiled in compabs_analysis.ipynb)
```{r}
# import dataframes
df_block = read.csv('../results/csv/df_block.csv')
df_chat = read.csv('../results/csv/df_chat.csv')
df_trial = read.csv('../results/csv/df_trial.csv')
df_exit = read.csv('../results/csv/df_exit.csv')

df_block$repNum = as.numeric(as.character(df_block$repNum))
df_chat$trialNum = as.numeric(as.character(df_chat$trialNum))
df_chat$repNum = as.numeric(as.character(df_chat$repNum))

df_trial <- transform(df_trial, trialScore = ifelse(is.na(trialScore), score, trialScore)) #fix score variable name change from livetest0 to pilots
#Group stimuli into scenes
df_trial = df_trial %>%
    dplyr::mutate(towerSet = case_when((leftTarget == 'L' | rightTarget == 'L')
                              & (leftTarget == 'Pi' | rightTarget == 'Pi')~ 'L/Pi',
                                (leftTarget == 'L' | rightTarget == 'L')
                            & (leftTarget == 'C' | rightTarget == 'C') ~ 'L/C', TRUE~'C/Pi'))
df_block = df_block %>%
    dplyr::mutate(towerSet = case_when((leftTarget == 'L' | rightTarget == 'L')
                              & (leftTarget == 'Pi' | rightTarget == 'Pi')~ 'L/Pi',
                                (leftTarget == 'L' | rightTarget == 'L')
                            & (leftTarget == 'C' | rightTarget == 'C') ~ 'L/C', TRUE~'C/Pi'))
df_trial$trialNum = as.numeric(as.character(df_trial$trialNum))
df_trial$repNum = as.numeric(as.character(df_trial$repNum))
```

#### Find GameIDs that satisfy exclusion criteria
```{r}
 
#Preprocessing ensures all dyads in these CSVs have completed all trials

#How many dyads fulfill 75% Accuracy on 75% of trials
games75 = df_trial %>% 
  group_by(gameid, trialNum) %>% 
  filter(trialScore > 75  & repNum != 'practice') %>%
  group_by(gameid)%>% 
  tally %>% 
  filter(n/12 >=0.75) %>% 
  distinct(gameid)

#How many dyads said they were confused <-- this is probably inverse coded...
gamesConfused = df_exit %>% 
  filter(confused == 'yes') %>% 
  distinct(gameid)

#How many dyads said they spoke English
gamesEnglish = df_exit %>% 
  filter(nativeEnglish == 'yes') %>% 
  distinct(gameid)

gamesToKeep = intersect(games75, gamesConfused, gamesEnglish)
```

#### Get count of failed practice trials
```{r}
View(df_trial %>% mutate(keepGame = gameid %in% gamesToKeep$gameid) %>% filter(is.na(trialNum)) %>% group_by(gameid, keepGame) %>% tally())
```

#### Plot first order analyses (word-block-message-score/repNum)
##### Word count/char count per repNum and trialNum
```{r}
df_chat$wordCount = sapply(strsplit(tolower(df_chat$content), " "), length)
df_chat$charCount =  nchar(tolower(df_chat$content))
df_chat$repNum = as.numeric(as.character(df_chat$repNum))
df_chat$trialNum = as.numeric(as.character(df_chat$trialNum))
```
```{r}
chat_grouped = df_chat %>% 
  dplyr::select(gameid,repNum, wordCount) %>% 
  subset(gameid %in% gamesToKeep$gameid) %>% 
  group_by(gameid,repNum) %>% 
  summarise(wordCount = sum(wordCount)) %>% 
  group_by(repNum) %>% summarise(wordCount = mean(wordCount)) %>% 
  drop_na()

chat_dyad = df_chat %>% 
  dplyr::select(gameid,repNum, wordCount) %>% 
  subset(gameid %in% gamesToKeep$gameid) %>%
  group_by(gameid,repNum) %>% 
  summarise(wordCount = sum(wordCount)) %>% 
  drop_na() #remove practice trials

ggplot(chat_dyad,  aes(x = repNum, y = wordCount))+
  geom_line(aes(group = gameid), alpha = 0.3)+
  geom_line(data =chat_grouped, aes(x = repNum, y = wordCount), size = 2, color = 'red')+
  #theme_bw()+
  xlab('Repetition Number')+
  ylab('Number of Words per Trial')
ggsave("WordCount.pdf",width = 5, height = 7)

```

```{r}
df_chat %>% 
  dplyr::select(gameid,repNum,charCount) %>% 
  group_by(gameid,repNum) %>% 
  summarise(charCount = sum(charCount)) %>% 
  group_by(repNum) %>% summarise(charCountAvg = mean(charCount)) %>% 
  ggplot(aes(x = repNum, y = charCountAvg)) + geom_line()
```

##### Blocks placed, Score, etc.
```{r}
#Average score per rep
score_grouped = df_trial %>% 
  dplyr::select(gameid,repNum, trialScore) %>% 
  subset(gameid %in% gamesToKeep$gameid) %>% 
  group_by(repNum) %>% summarise(Score = mean(trialScore)) %>% 
  drop_na()

score_dyad = df_trial %>% 
  dplyr::select(gameid,repNum, trialScore) %>% 
  subset(gameid %in% gamesToKeep$gameid) %>% 
  group_by(gameid,repNum) %>% 
  summarise(Score = mean(trialScore)) %>% 
  drop_na() #remove practice trials

ggplot(score_dyad,  aes(x = repNum, y = Score))+
  geom_line(aes(group = gameid), alpha = 0.3)+
  geom_line(data =score_grouped, aes(x = repNum, y = Score), size = 2, color = 'red')+
  #theme_bw()+
  xlab('Repetition Number')+
  ylab('Reconstruction Accuracy')
ggsave("score.pdf",width = 5, height = 7)
```

```{r}
#Blocks placed per rep
block_grouped = df_block %>% 
  dplyr::select(gameid,repNum, trialNum, turnNum) %>% 
  subset(gameid %in% gamesToKeep$gameid) %>% 
  group_by(gameid, repNum, trialNum, turnNum) %>% summarise(n = n()) %>% 
  group_by(gameid, repNum) %>% summarise(blocksPlaced = mean(n)) %>% 
  group_by(repNum) %>% summarise(blocksPlaced = mean(blocksPlaced)) %>% 
  drop_na()

block_dyad = df_block %>% 
  dplyr::select(gameid,repNum, trialNum, turnNum) %>% 
  subset(gameid %in% gamesToKeep$gameid) %>% 
  group_by(gameid, repNum, trialNum, turnNum) %>% summarise(n = n()) %>% 
  group_by(gameid, repNum) %>% summarise(blocksPlaced = mean(n)) %>% 
  drop_na()

ggplot(block_dyad,  aes(x = repNum, y = blocksPlaced))+
  geom_line(aes(group = gameid), alpha = 0.3)+
  geom_line(data =block_grouped, aes(x = repNum, y = blocksPlaced), size = 2, color = 'red')+
  #theme_bw()+
  xlab('Repetition Number')+
  ylab('Number of Blocks per Instruction')
  #theme(axis.text.x = element_blank())
ggsave("blocksplaced.pdf",width = 5, height = 7)
```
### Join dfs to get score correlations


### Visualize word count over time (trialNum, repNum)
```{r}
a = df_chat %>% 
  dplyr::select(gameid,trialNum,repNum,wordCount) %>% 
  group_by(gameid,trialNum, repNum) %>% 
  summarise(wordCount = sum(wordCount))

b = df_trial %>% dplyr::select(gameid, trialNum, repNum, trialScore, towerSet) %>% 
  group_by(gameid, trialNum, repNum, towerSet) %>% 
  summarise(trialScore = max(trialScore)) #to deal with multiple practices

c = merge(a, b, by = c("gameid", "trialNum", "repNum"))

d = merge(c,gamesToKeep, by = "gameid", all.y = TRUE)

d  %>% 
  ggplot(aes(x = repNum, y = wordCount, color = repNum))+
  geom_point()+
  geom_smooth()
```


## Fit linear regression model to predict word count from repetition number
```{r}
lme = lmer(data = c, wordCount ~ repNum + (1 | gameid) + (1 | towerSet))
summary(lme)  

```


```{r}
block_dyad = df_block %>% 
  dplyr::select(gameid,repNum, trialNum, turnNum, towerSet) %>% 
  subset(gameid %in% gamesToKeep$gameid) %>% 
  group_by(gameid, repNum, trialNum, turnNum, towerSet) %>% summarise(n = n()) %>% 
  group_by(gameid, repNum, towerSet) %>% summarise(blocksPlaced = mean(n)) %>% 
  drop_na()
lme = lmer(data = block_dyad, blocksPlaced ~ repNum + (1 | gameid) + (1| towerSet))
summary(lme)   
```
## Fit linear regression model to predict accuracy from repetition number
```{r}
dat_trial = df_trial %>% subset(gameid %in% gamesToKeep$gameid)
lme = lmer(data = dat_trial, trialScore ~ repNum + (1 | gameid) + (1| towerSet))
summary(lme)   
```